### 2010-10-17 ms/titelblattSUPAERO.tex
added report and presentation held for supaero

\vspace*{3.3cm}
\begin{minipage}[c]{11cm}
{\LARGE\bf 
Simuation of high enthalpy flow in porosities using SPH}
\end{minipage}

\vspace*{0.8cm}
Oliver Oberinger\\

\vspace*{2.8cm}
{\bfseries Diplomarbeit}

\vspace*{1.2cm}
%\large
\normalsize
\vfill
\begin{tabular}{ll}
Betreuer: & ~Prof. Hans G. Hornung (Caltech)\\
\ & \ Dipl.-Ing. Sergey Litvinov (TUM)\\
 \\
Ausgabe: & 15.\ Juni 2010\\
Abgabe: & 15.\ Dezember 2010\\
\end{tabular}

>>>>

\vspace*{3.3cm}
\begin{minipage}[c]{11cm}
{\LARGE\bf 
Simulation of high enthalpy flow in porosities using SPH}
\end{minipage}

\vspace*{1.0cm}

Oliver Oberinger\\
\vspace*{1.0cm}
{\bfseries Intermediate version of Master's Thesis}\\
\vspace*{0.5cm}
for presentation at \\
\vspace*{0.3cm}
Institut Sup\'{e}rieur de l'A\'{e}ronautique et de l'Espace\\

\begin{minipage}[c]{.25\textwidth}
	\includegraphics[width=3cm,clip=]{LOGO/LogoISAE}\\
\end{minipage}
\\
\vspace*{0.1cm}
responsible at ISAE: J\'{e}r\'{e}mie Gressier (Professeur SUPAERO)

\vspace*{1.2cm}
%\large
\normalsize
\vfill
\begin{tabular}{ll}
Advisors: & ~Prof. Hans G. Hornung (Caltech)\\
\ & \ Dipl.-Ing. Sergey Litvinov (TUM)\\
\ & \ Prof. Dr.-Ing. Nikolaus A. Adams (TUM)\\
 \\
\end{tabular}
